---
title: "LCL_data_pruning"
output: html_notebook
---

This notebook reads five .Rda files created by LCL_data_merging.Rmd.  It investigates the data and drops both observations and variables, with the goal of creating a dataset for analysis with:

- Observations that are award (i.e. not IDV) contracts only
- Observations that are completed (i.e. not ongoing) contracts only
- Variables that exist at the award of the contract (i.e. are prior to performance)

Setup:
```{r}
library(magrittr)
library(tidyverse)

```

construct index:

```{r}
# load("contracts_1.Rda")
# var_names <- names(CompleteContracts)
# rda_index <- rep("contracts_1.Rda", length(names(CompleteContracts)))
# rm(CompleteContracts)
# 
# load("contracts_2.Rda")
# var_names <- c(var_names, names(CompleteContracts))
# rda_index <- c(rda_index, rep("contracts_2.Rda", length(names(CompleteContracts))))
# rm(CompleteContracts)
# 
# load("contracts_3.Rda")
# var_names <- c(var_names, names(CompleteContracts))
# rda_index <- c(rda_index, rep("contracts_3.Rda", length(names(CompleteContracts))))
# rm(CompleteContracts)
# 
# load("contracts_4.Rda")
# var_names <- c(var_names, names(CompleteContracts))
# rda_index <- c(rda_index, rep("contracts_4.Rda", length(names(CompleteContracts))))
# rm(CompleteContracts)
# 
# load("contracts_5.Rda")
# var_names <- c(var_names, names(CompleteContracts))
# rda_index <- c(rda_index, rep("contracts_5.Rda", length(names(CompleteContracts))))
# rm(CompleteContracts)
# 
# var_index <- data.frame(cbind(var_names, rda_index))
# 
# save(var_index, file = "index.Rda")

load("index.Rda")

```

Restrict to non-IDV contracts:

```{r}
load("contracts_1.Rda")
load("greg_IDV_code.Rda")
```


```{r}
CompleteContracts %<>% left_join(asdf)
```

```{r}
CompleteContracts %<>% filter(IDV == "Def/Pur")
rm(asdf)
```


Subset to closed contracts:

```{r}
CompleteContracts%<>%
  filter(
    IsClosed == 1 |
    LastUltimateCompletionDate <= as_date("2013-09-30") |
    LastCurrentCompletionDate <= as_date("2012-10-01"))  
```



Merge next file:

```{r}
dataset <- CompleteContracts
load("contracts_2.Rda")
dataset %<>% left_join(CompleteContracts)
```



Next:
```{r}
rm(CompleteContracts)
load("contracts_3.Rda")
```


```{r}
dataset %<>% left_join(CompleteContracts)
```

Next file:


```{r}
rm(CompleteContracts)
load("contracts_4.Rda")
```


```{r}
dataset %<>% left_join(select(CompleteContracts, -IsIDV))
```


final one:

```{r}
rm(CompleteContracts)
load("contracts_5.Rda")
```


```{r}
dataset %<>% left_join(CompleteContracts)
rm(CompleteContracts)
```




Remove non-prior features:
```{r}
dataset %<>%
  select(
    -Action.Obligation,
    -ChangeOrderBaseAndAllOptionsValue,
    -ChangeOrderObligatedAmount,
    -Pricing.Mechanism.Code,
    -ObligatedAmountIsFixedPrice,
    -IsFixedPrice,
    -ObligatedAmountIsCostBased,
    -IsCostBased,
    -ObligatedAmountIsCombination,
    -IsCombination,
    -ObligatedAmountIsIncentive,
    -IsIncentive,
    -ObligatedAmountIsAwardFee,
    -IsAwardFee,
    -ObligatedAmountIsFFPorNoFee,
    -IsFFPorNoFee,
    -ObligatedAmountIsFixedFee,
    -IsFixedFee,
    -ObligatedAmountIsOtherFee,
    -IsOtherFee,
    -pIsFixedPrice,
    -pIsCostBased,
    -Is_NA_ObligatedAmountIsFixedPrice,
    -Is_NA_ObligatedAmountIsCostBased,
    -pIsCombination,
    -Is_NA_ObligatedAmountIsCombination,
    -FixedOrCost,
    -pIsIncentive,
    -Is_NA_ObligatedAmountIsIncentive,
    -pIsAwardFee,
    -Is_NA_ObligatedAmountIsAwardFee,
    -pIsFFPorNoFee,
    -Is_NA_ObligatedAmountIsFFPorNoFee,
    -pIsFixedFee,
    -Is_NA_ObligatedAmountIsFixedFee,
    -pIsOtherFee,
    -Is_NA_ObligatedAmountIsOtherFee)
```


```{r}
dataset %<>% select(
  -IsClosed,
  -LastSignedLastDateToOrder,
  -LastUltimateCompletionDate,
  -LastCurrentCompletionDate,
  -SumOfnumberOfActions,
  -ContractBaseAndAllOptionsValue,
  -ContractBaseAndExercisedOptionsValue,
  -maxoffiscal_year,
  -IsIDV,
  -SystemEquipmentInterlinked,
  -ContractingOfficePlatformInterlinked,
  -Is_NA_ContractingOfficePlatformInterlinked,
  -Is_NA_SystemEquipmentInterlinked,
  -LinkedContracts,
  -ChangeOrderBaseAndExercisedOptionsValue,
  -NewWorkBaseAndAllOptionsValue,
  -NewWorkBaseAndExercisedOptionsValue,
  -NewWorkObligatedAmount,
  -IDV,
  -PlaceCountryISO3,
  -ObligatedAmountIsInternational,
  -AnyInternational,
  -IsInternational,
  -pIsInternational,
  -is_NA_ObligatedAmountIsInternational,
  -IsModified,
  -SumOfisChangeOrder,
  -MaxOfisChangeOrder,
  -SumOfisNewWork,
  -MaxOfisNewWork)
```


```{r}
dataset %<>%
  select(
    -pChangeOrderObligated,
    -PlatformPortfolio,
    -ObligatedAmountIsAir,
    -ObligatedAmountIsEnC,
    -ObligatedAmountIsFRSnC,
    -ObligatedAmountIsLand,
    -ObligatedAmountIsMnS,
    -ObligatedAmountIsOtherPP,
    -ObligatedAmountIsVessel,
    -ObligatedAmountIsWnA,
    -ProductOrServiceArea,
    -SimpleArea,
    -ObligatedAmountIsProducts,
    -ObligatedAmountIsServices,
    -ObligatedAmountIsRnD,
    -MaxOfIsPossibleSoftwareEngineering,
    -pIsProducts,
    -Is_NA_ObligatedAmountIsProducts,
    -pIsServices,
    -Is_NA_ObligatedAmountIsServices,
    -pIsRnD,
    -Is_NA_ObligatedAmountIsRnD,
    -pIsLand,
    -Is_NA_ObligatedAmountIsLand,
    -pIsVessel,
    -Is_NA_ObligatedAmountIsVessel,
    -pIsAir,
    -Is_NA_ObligatedAmountIsAir,
    -pIsEnC,
    -Is_NA_ObligatedAmountIsEnC,
    -pIsFRSnC,
    -Is_NA_ObligatedAmountIsFRSnC,
    -pIsMnS,
    -Is_NA_ObligatedAmountIsMnS,
    -MaxOfIsUndefinitizedAction,
    -NumberOfOffersReceived,
    -IsFullAndOpen,
    -IsSomeCompetition,
    -ObligatedAmountIsSomeCompetition,
    -IsOnlyOneSource,
    -IsFollowonToCompetedAction,
    -multipleorsingleawardidc,
    -AddMultipleOrSingleAwardIDC,
    -AwardOrIDVcontractActionType)
```


```{r}
dataset %<>%
  select(
    -pIsOtherPP,
    -Is_NA_ObligatedAmountIsOtherPP,
    -Customer,
    -SubCustomer,
    -ObligatedAmountIsArmy,
    -ObligatedAmountIsNavy,
    -ObligatedAmountIsAirForce,
    -ObligatedAmountIsOtherDoD,
    -pIsArmy,
    -pIsNavy,
    -pIsAirForce,
    -pIsOtherDoD,
    -Is_NA_ObligatedAmountIsArmy,
    -Is_NA_ObligatedAmountIsNavy,
    -Is_NA_ObligatedAmountIsOtherDoD,
    -Is_NA_ObligatedAmountIsAirForce,
    -IsLabeledPricing,
    -Fee)
```


drop missing outcomes
```{r}
dataset %<>% filter(
  !(is.na(dataset$pChangeOrderUnmodifiedBaseAndAll) & is.na(dataset$IsTerminated)))
```


```{r}
save(dataset, file = "clean_dataset.Rda")
```
